Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-05-28 sources/bmc_template_submission/bmc_article.tex
some moretiny edits

\section*{Acknowledgements}
We thank the members of the current OpenTree development team (MH, KC, MTH, and JA),
and the ``short bar" Science
and Engineering Building 1, UCM, Bloise-McTavish joint lab paper discussion group for valuable
comments on this manuscript. We also thank the valuable comments of David Posada, Rutger Vos,
and an anonymous reviewer that greatly improved an earlier version of this manuscript.

>>>>

\section*{Acknowledgements}
We thank the members of the current OpenTree development team (MH, KC, BR, and JA),
and the ``short bar" Science
and Engineering Building 1, UCM, Blois-McTavish joint lab paper discussion group for valuable
comments on this manuscript. We also thank the valuable comments of David Posada, Rutger Vos,
and an anonymous reviewer that greatly improved an earlier version of this manuscript.
